---
title: "Visualization Final Report"
author: "Jacob Saindon"
format: 
  html: 
    theme: darkly
---

# Data Visualization Block Report

## The Visualization

```{r}
library(tidyverse)
library(ggrepel)
library(showtext)
  font_add_google(name = "Nunito", family = "nunito")
  showtext_auto()
  set.seed(500)
```

Source: https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-01-25/readme.md

```{r}
ratings <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/ratings.csv')
```

```{r}
#| fig-width: 8
#| fig-height: 8
rate_plot<-ggplot(subset(ratings, rank %in% c(1:50)),aes(x=average,y=reorder(name,-rank),size=users_rated))+
  geom_point()+
  scale_x_continuous(limits=c(7.5, 9),position="top")+
  scale_y_discrete(position="left")+
  theme_minimal()+
  theme(legend.position="top", plot.title=element_text(size = 28), plot.subtitle=element_text(size = 20),text=element_text(size=16))+
  labs(family="nunito",
       x="Average Rating (out of 10)",
       y="Game Ranking (1st ranked at top, 50th at bottom)",
       size="Number of Reviews",
       title="Top 50-Ranked Board Games by Rating and Number of Reviews",
       subtitle="According to Board Game Geek, 2022",
       caption="Visualized by Jacob Saindon, Feb. 2023\nData from TidyTuesday by way of Board Game Geek\nhttps://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-01-25/readme.md")

rate_plot
```

## The Report

What data you're plotting, and what its source is.

-   The chart is visualizing the Top 50-ranked games according to rating site Board Game Geek (BGG), top-to-bottom, displayed on the x-axis by the games' average rating out of 10. The size of the dot represents the total volume of reviews on BGG.

Do you have a sketch of what you'd like the plot to look like?

-   Curious about the relationship between game rankings from BGG (a respected rater) and the volume/rating of games

What decisions did you make in creating the plot (e.g. labels, colors, geometries, plot orientation, etc.)

-   Label by individual games, not in aggregate. Because dataset does not include categories (such as Eurogames v. Amerigames). No colors, since no categorization. Size as a visual variable to correspond to number of reviews. Rating on the x-axis to keep game names more visible on the y-axis. Labeled at the top because the chart is long to incorporate all 50 games.
-   Ordering games from #1 ranked at the top to #50 at the bottom. Selecting only top 50 to try and keep the chart legible. Setting the x-breaks at 7.5 and 9 to show variation but not over-emphasize the difference.

Why did you make those decisions?

Does the final plot fall short of your ultimate vision in any way?

-   I would have liked to include the Y-axis title on the right-hand side to separate it from the board games names.

-   There are some slight imperfections in terms of visualization overlaps that I am not certain how to correct.
